---
title: "Twitter_COVID_Gender Analysis"
author: "Arnab Dey"
date: "4/14/2021"
output: html_document
---

```{r}
library(tidyverse)
```

```{r function to extract hashtags}
extract_hashtags <- function(data, text) {
  hash_tags <- as.data.frame(unlist(str_extract_all(data$text, "#\\w+")))
  colnames(hash_tags) <- "words"
  hash_tags <- as.data.frame(str_remove_all(hash_tags$words, "[#]"))
  colnames(hash_tags) <- "words"
  hash_tags <- hash_tags %>% 
    count(words)
  return(hash_tags)
}
```

# Read output of the gensim model
```{r}
df_topics <- read.csv("output.csv")
```

# Order topics by number of tweets in that topic
```{r}
df_topic_num <- df_topics %>% 
  count(Dominant_Topic) %>% 
  arrange(-n) %>% 
  mutate(topic_num = row_number(-n)) %>% 
  select(-n)
  
df_topics <- df_topics %>% 
  left_join(df_topic_num, by = "Dominant_Topic") %>% 
  mutate(date = as.Date(created_at))

```


## Label Topics

```{r}
df_topics <- df_topics %>% 
    mutate(topic_label = factor(topic_num, 
          levels = c(1:10), 
          labels = c("Topic-1: Child-marriage and \nits impacts on education ",
            "Topic-2: Supporting young \nwomen to learn ",
            "Topic-3: Access to education \nfor crisis-affected girls ",
            "Topic-4: Education for \nwomen empowerment ",
            "Topic- 5: Online events around \ngender equity in education ",  
            "Topic-6: Gender disparities \nin educational attainment ",
            "Topic-7: Food insecurity during \nCOVID-19 & its impact on girls ",
            "Topic-8: Celebrating women \nin Science ",
            "Topic-9: Online abuse and \nharrassment faced by girls ", 
            "Topic-10: School Related \nGender Based Violence ")))

```


# Create Datasets for the output plots

## Dataframe for wordcloud
```{r}
df_ana_full <-read_excel("twitter_data.xlsx")       # Specify the file downloaded from twitter
df_ana_full <- as.data.frame(df_ana_full[,c(3,4,5)])
df_wordcloud <- extract_hashtags(df_ana_full, text)
write.csv(df_wordcloud, "Datasets/data_wordcloud.csv")
```

## Dataframe for bargraph

```{r}
df_plot_2 <- df_topics %>% 
  select(topic_label) %>% 
  count(topic_label) 

write.csv(df_plot_2, "Datasets/data_fig_2.csv")
```

## Dataframe for number of tweets over time across topics

### create a dataframe of topic_num and labels
```{r}
df_topic_num_label <- df_topics %>% 
  distinct(topic_num, topic_label) %>% 
  arrange(topic_num)
```

### Create a dataframe with selected topics for in-depth analysis

#### Topics selected for in-depth analysis: 1, 3, 6, 7, 9 and 10

```{r}
df_topics_select <- df_topics %>% 
  filter(topic_num == 1 | topic_num == 3 | topic_num == 6 | topic_num == 7 | topic_num > 8)
```


### Create dataframe for the plot
```{r}
df_plot_3 <- df_topics_select %>% 
  count(date, topic_num) %>% 
  left_join(df_topic_num_label, by = "topic_num") %>% 
  arrange(topic_num, date)

write.csv(df_plot_3, "Datasets/data_fig_3.csv")
```

